Model matters with restricted Boltzmann machines

### 2016-12-11 presentations/amherst/slides.Rmd
add contct info

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan, Daniel Nordman, and Stephen Vardeman
shortname: Kaplan, et al.
institute: ajkaplan@iastate.edu
date: "December 20, 2016"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

- While RBMs are thought to be useful for classification, in the context of generative statistical models, RBMs are a poor fit due to *near-degeneracy*, *S-instability*, and w*uninterpretability*.
- Rigorous fitting methodology is difficult due to the dimension of the parameter space coupled with the size of the latent variable space.
- For a RBM model with enough hidden variables, any distribution for the visibles can be approximated arbitrarily well [@le2008representational; @montufar2011refinements; and @montufar2011expressive]. 
    - The empirical distribution of a training set of vectors of visibles is the best fitting model for observed cell data. 
    - There can be no "smoothed distribution" achieved in fitting a RBM model of sufficient size with a rigorous likelihood-based method.

@@

>>>>

---
title: "Model matters with restricted Boltzmann machines"
shorttitle: "Model matters with RBMs"
author: Andee Kaplan, Daniel Nordman, and Stephen Vardeman
shortname: Kaplan, et al.
institute: |
    | Iowa State University
    | ajkaplan@iastate.edu
shortinstitute: ajkaplan@iastate.edu
date: |
  | December 20, 2016
  | 
  |
  | Slides available at <http://bitly.com/kaplan-amherst>
shortdate: "December 20, 2016"
output: 
  beamer_presentation:
    template: latex/beamer.tex
    includes:
      in_header: latex/front-matter.tex
theme: CambridgeUS
bibliography: latex/refs.bib
fig_caption: true
nocite: |
    @salakhutdinov2009deep, @kaiser2007statistical
---

@@

- While RBMs are thought to be useful for classification, in the context of generative statistical models, RBMs are a poor fit due to *near-degeneracy*, *S-instability*, and *uninterpretability*.
- Rigorous fitting methodology is difficult due to the dimension of the parameter space coupled with the size of the latent variable space.
- For a RBM model with enough hidden variables, any distribution for the visibles can be approximated arbitrarily well [@le2008representational; @montufar2011refinements; and @montufar2011expressive]. 
    - The empirical distribution of a training set of vectors of visibles is the best fitting model for observed cell data. 
    - There can be no "smoothed distribution" achieved in fitting a RBM model of sufficient size with a rigorous likelihood-based method.

@@

# Thank you

* Slides -- <http://bitly.com/kaplan-amherst>

* Contact
    * Email -- <ajkaplan@iastate.edu>
    * Twitter -- <http://twitter.com/andeekaplan>
    * GitHub -- <http://github.com/andeek>
